A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-11 manuscript.Rmd
fix typo

You can also manually edit the `Dockerfile` by amending the file `.repro/Dockerfile_manuel` to install software beyond R packages.
Remember to run `repro::automate()` after you made edits to `.repro/Dockerfile_manuel`.
We recomend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.

>>>>

You can also manually edit the `Dockerfile` by amending the file `.repro/Dockerfile_manual` to install software beyond R packages.
Remember to run `repro::automate()` after you made edits to `.repro/Dockerfile_manual`.
We recomend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.
